---
title: 'Sep 17 Synchronous Session'
author: 'Data Science for Biomedical Informatics (BMIN503/EPID600)'
output: 
  html_document:
    theme: cerulean
    highlight: pygments
---

***

### COVID in Philadelphia

1. Load data frames called `covid.jul` and `covid.aug` corresponding to covid test results reported by the Philadelphia Department of Public Health on July 7 and August 11, 2020 that are in files `phl_covid_tests_7.7.20.txt` and `phl_covid_tests_8.11.20.txt`, respectively.

```{r, eval = TRUE}
setwd("~/EPID600/PHLcovid")
CovJul <- read.table("phl_covid_tests_7.7.20.txt", sep="\t", header=TRUE)
CovAug <- read.table("phl_covid_tests_8.11.20.txt", sep="\t", header=TRUE)
Cov <- rbind(CovJul, CovAug)

```

2. How many COVID-19 test results had been reported in Philadelphia by August 11? 
```{r, eval = TRUE}
sum(CovAug$count)

```

3. What zip code had the greatest number of positive tests by August 11?
```{r, eval = TRUE}
library(dplyr)
Pos.cov <- subset(CovAug, covid_status == "POS") %>%
    group_by(zip_code) %>% 
    summarize(total = sum(count))

paste(Pos.cov[which.max(Pos.cov$total), "zip_code"])
```

4. Create a function `most.neg` that returns the zip code with the greatest number of negative tests along with that number as a data frame. Use the function to get this output for July 7 and Aug 11.
```{r, eval = TRUE}
most.neg <- function(df){
Neg.cov <- subset(df, covid_status == "NEG") %>%
  group_by(zip_code) %>% 
  summarize(total = sum(count))  
output <- data.frame(Neg.cov[which.max(Neg.cov$total), "zip_code"], Neg.cov[which.max(Neg.cov$total), "total"])
output
}

most.neg(CovAug)
most.neg(CovJul)

```


***